### 2020-01-25 introduction.tex
Gustavo edits

The value of the differential comparison lies in a few key points.  First, this is a measure that does not reward a tool that produces too many false positives.  The tool cannot simply flag all code as having a problem or it will perform poorly at the task of \emph{distinguishing} the mutated code from non-mutated (and presumably at least \emph{more} correct) code.  Based on verification and testing uses of mutation, it is safe to say that at least 50, and likely 60-70\% or more, of mutants that are not semantically equivalent to the original code are actually fault-inducing, so the task presented to a static analysis tool is the generalization of the task we ideally expect static analysis to perform:  to identify faulty code, without executing it, and, most critically, \emph{to distinguish faulty from correct code}.  Obviously, many faults cannot be identified statically without a complete specification, or without unreasonable analysis cost and precision, but the measure of performance here is meant to be mostly \emph{relative} to other tools applied to the same code; this is primarily a \emph{differential} approach.  In other words, a key notion is that while most mutants cannot be detected statically, the ones that are tend to be \emph{true positives}: if they were real code changes, they would be faults.

>>>>

The value of the differential comparison lies in a few key points.  First, this is a measure that does not reward a tool that produces too many false positives.  The tool cannot simply flag all code as having a problem or it will perform poorly at the task of \emph{distinguishing} the mutated code from non-mutated (and presumably at least \emph{more} correct) code.  Based on verification and testing uses of mutation, it is safe to say that usually at least 40\%, and often 50-60\% or more, of mutants are not semantically equivalent to the original code, and are actually fault-inducing \cite{TCE,groce2015verified,groce2018verified,impactEquiv,smith2009should}, so the task presented to a static analysis tool is the generalization of the task we ideally expect static analysis to perform:  to identify faulty code, without executing it, and, most critically, \emph{to distinguish faulty from correct code}.  Obviously, many faults cannot be identified statically without a complete specification, or without unreasonable analysis cost and precision, but the measure of performance here is meant to be mostly \emph{relative} to other tools applied to the same code; this is primarily a \emph{differential} approach.  In other words, a key notion is that while most mutants cannot be detected statically, the ones that are tend to be \emph{true positives}: if they were real code changes, they would be faults.

### 2020-01-25 prioritizing.tex
Gustavo edits

We do not claim this is an optimal, or even tuned, metric.  It
provided useful results for a different problem, ranking mutants in an
effort similar to that of Groce et
al. \cite{groce2015verified,groce2018verified} to examine unkilled
mutants for a smart contract library tested using the Echidna fuzzer,
and we simply adopted it for our differential mutation analysis.
Devising a better metric is left as future work, we only wish to show
that even a hastily-devised and somewhat arbitrary metric provides
considerable advantage over wading through an un-ordered list of
mutants, and introduce the idea of using FPF for mutants, not just tests.

>>>>

We do not claim this is an optimal, or even tuned, metric; in the long run, it may be completely replaced.  It did
provide useful results for a different problem, ranking mutants in an
effort similar to that of Groce et
al. \cite{groce2015verified,groce2018verified} to examine unkilled
mutants for a smart contract library tested using the Echidna fuzzer \cite{echidna-code},
and we simply adopted it for our differential mutation analysis.
Devising a better metric is left as future work, we only wish to show
that even a hastily-devised and somewhat arbitrary metric provides
considerable advantage over wading through an un-ordered list of
mutants, and introduce the idea of using FPF for mutants, not just tests.
